Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-11 article.tex
eod back up

  The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors like soil management practices show regional variation. The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies. It is important to acknowledge that this analysis is preliminary and further work is required to cover the numerous wine regions across Australia and globally. Previous studies have also illustrated similar regional differences, underscoring the complexity and necessity of localised sustainability assessments.

@@

  The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact. For instance, the Coonawarra-specific model demonstrates that changes in water management practices have a higher sensitivity to environmental impact compared to the generic model. This highlights the critical areas where regulatory and environmental interventions could have the most substantial effect.

>>>>

The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel. The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies. It is important to acknowledge that this analysis also illustrates that further work would be required to describe other regions or specific vineyards.

The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact. For instance, the Coonawarra-specific model demonstrates that the significance that pest/disease, and agrochemicals have a higher sensitivity to environmental impact compared factors such as green house gas emissions. Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target.

@@
